Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-31 Scripts/Initial_Analysis.Rmd
Created code for ToE tempr

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis",
  "cowplot",
  "rfishbase",
  "stargazer" # For nice lm tables
)

@@

EEZ_CellID <- my_path("G", extra_path = "Spatial/DBEM", name="EEZ_CellID.xlsx", read = TRUE) %>%
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

# SAU name relatioal table (Fish For Visa)
sau_clean_names <- my_path("G", extra_path = "Spatial/SAU/", name="matching_names.csv", read = TRUE)

@@

getEnvVar=function(yr,ensemble,Variable){

  filepath <- paste("Z:/DATA/Environmental data/GFDL_CMIP5_Large_Ensemble/ens",ensemble,"",sep="/")

  if(Variable == "sst"){
    sst = paste("SST_",yr,".txt",sep="")
    read_me_sst <- paste(filepath,sst,sep="")[1]
    data <- read.csv(read_me_sst,header=F)

  if(Variable == "botom"){
    botom = paste("botom_",yr,".txt",sep="")
    read_me_botom <- paste(filepath,botom,sep="")[1]
    data <- read.csv(read_me_botom,header=F)
  }

@@

  getTemp <- data %>% 
    mutate(ensemble = ensemble)
}

@@

TempEmer <- function(Hist_y = 2005){ # The LAST year of Historical data

@@

@@

# Get taxon list
Taxon_list_emer <- list.files(my_path("R",extra_path = "Emergence_2005"))

# clean names for function
Taxon_list_emer <- gsub("_.*","",Taxon_list_emer)

# SAU exploited species list
Exploited_spp_list <- my_path("G","SAU","exploited_species_list.csv",read = T) %>%
  clean_names() %>% 
  pull(taxon_name)

# Get habitat preference from fishbase
Spp_env_pref <- rbind(species(Exploited_spp_list, #species from rfishbase package
                              fields = species_fields$habitat[4])
                      ) %>% 
  mutate(taxon_name = Exploited_spp_list) %>% 
  left_join(my_path("G","SAU","exploited_species_list.csv", read = T) %>%
              clean_names(),
            by = "taxon_name")

@@

# Clean names to match data
Matching_names <- my_path("G","Spatial/SAU", "matching_names.csv", read = T) %>% 
  rename(eezid = eez_id)

Fishing_names <- Matching_names %>% 
  group_by(sau_fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  select(-n)

# eez_centroids
Eez_centroids <- my_path("D", extra_path = "Spatial/", name="eez_centroids.csv", read = TRUE) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(eezid,latitude,longitude)

# Species depth clasification (SAU-fishbase)
Spp_depth <-fread(paste(my_path("D"),"SAU/SppTaxonName.csv", sep ="")) %>% 
  clean_names()

# Temperature Time of Emergence
Toe_temp <- left_join(my_path("D","Climate", "ToE_sst.csv", read = T),
                      my_path("D","Climate", "ToE_bottemp.csv", read = T)
                      ) %>% 
  clean_names()

# Biogeographic regions (from Rey 2020)
Biogeo_reg <-fread(paste(my_path("D"),"Climate/SPATIAL_PARTITION_OCEAN.csv", sep ="")) %>% 
  clean_names() %>% 
  rowid_to_column("index")

# Get eez to index relational data
EEZ_CellID <- my_path("G", extra_path = "Spatial/DBEM", name="EEZ_CellID.xlsx", read = TRUE) %>%
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

Eez_biogeo <- EEZ_CellID %>% 
  # filter(eezid == 191) %>% 
  left_join(Biogeo_reg,
       by = "index") %>% 
  # Deal with NaNs in data
  mutate(biome = ifelse(biome == "NaN",0,biome)) %>% 
  filter(biome > 0) %>% 
  # Get frequency of biome per index
  group_by(eezid,biome) %>% 
  summarise(nbiom=n()) %>% 
  # Select the more frequent biome per eez
  group_by(eezid) %>% 
  top_n(1,nbiom) %>% 
  ungroup() %>% 
  select(-nbiom) %>% 
  distinct(eezid, .keep_all = T) # Croatia is 1/2. We arbritary allocated the first one

# Species catch trend (from FishForVisa)

Catch_trend <- my_path("D","Species","Catch_trend.csv", read = T) %>% 
  clean_names() %>% 
  filter(taxon_key %in% Taxon_list_emer) %>% 
  rename(sau_fishing_entity = territory) %>% 
  left_join(Fishing_names,
            by = "sau_fishing_entity") %>% 
  filter(status != "No Trend") %>% 
  mutate(category = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
                         ifelse(status == "Max Exploited","Category B",
                                ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                         )
         )
  )

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_list_emer,"_emergence.txt",sep="")

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  # st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326)
  # sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
           aes(start_lon,
               start_lat,
               col = per_plot),
           size = 0.05,
           col = "gray80",
           shape = 20,
           stroke = 1.5) +
geom_path(data = subset(paths, time_step == time & per_plot > 0),
          aes(X,
              Y,
              group = interaction(line_id,subline_id),
              col = per_plot
          ),
          size = 0.3,
          lineend = "round",
          arrow = arrow(length = unit(0.008, "npc"),
                        ends = "first"),
          show.legend = NA) +
  my_ggtheme_m() +
scale_colour_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # option="magma",
  # direction = -1
) +
scale_fill_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # alpha = 0.8
  # option="magma",
  # direction = -1
) +
ggsave("./Figures/fig2ax.png",
       width = 12,
       height = 8,
       units = "in"
)

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  ) %>% 
  filter(!is.na(participation))

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id) %>% 
  filter(sovereignt != "Antarctica")

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_lat_",tresh_list[i],".png",sep = "")

  ## --------------- ##
  # Latitudinal plot
  ## --------------- ##

Eez_hist <- Eme_Res %>% 
  group_by(eezid,eez_name = sf_eez_name) %>% 
  left_join(Eez_centroid) %>% 
  filter(tresh == tresh_list[i]) %>% 
  group_by(latitude) %>% 
  summarise(
    number = n()
  ) %>% 
  group_by() %>% 
  mutate(RMean = rollmean(x = number, 
                          10, 
                          align = "center", 
                          fill = number
  )
  ) %>% 
  mutate(lab="lab") %>% 
  ggplot() +
  geom_area(
    aes(
      x = latitude,
      y = RMean,
      fill = lab,
      color = lab
    )
  ) +
  coord_flip() +
  scale_x_continuous("",
    limits = c(-50,80),
    breaks = c(-50,0,50,80)
  ) +
  scale_y_continuous(
    "Emerging stocks",
    limits = c(0, 124),
    breaks = c(0,62,124)

  ) +
  scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
  scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
  theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_text(size = 12, colour="black"),
    axis.title.x = element_text(size = 12, colour="black", face = "bold"),
    legend.position = ""
  );Eez_hist

  ## --------------- ##
  # Map
  ## --------------- ##

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-135,
             y = -69,
             label = "Participation (%)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

  ## --------------- ##
  # Combine plots and save them
  ## --------------- ##

  p <- ggdraw() +
    # ToE Latitudinal plot
    draw_plot(Eez_hist, x = 0.873, y = 0.13, width = 0.124, height = 0.77) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0, width = 0.95, height = 1)

  save_plot(
    name_save,
    p,
    base_height = 6,
    base_width = 12
  )

@@

### Tab.1 Explain the ToE

```{r multiple_reg, eval = F, echo = F}

# Possible explanatory variables

## Habitat association (DemersPelag)
## Dem Vs Pelagic (Dem_pel)
## SST time of Emer (Toe_sst)
## Stock Status [FishForVisa] (Catch_trend)
## Biogeographic location (Biogeo_reg)

# AIC value; model between predictive capacity and complexity (i.e., number of explanatory variables) is given by the model with lowest AIC value

# -------------------------------- #
#### Prepare data
# -------------------------------- #

Lm_data <- Eme_Res %>% # 19728
  filter(tresh == "Tresh_one") %>% # 11490
  left_join(Spp_depth) %>% 
  select(taxon_key,tresh,sf_eez_name,sau_fishing_entity,fishing_entity_id,emerging_yr,eezid,dem_pel) %>% 
  left_join(Toe_temp,
            by = c("eezid","tresh")
            ) %>% 
  left_join(Catch_trend,
            by = c("taxon_key","sau_fishing_entity","fishing_entity_id")
            ) %>% # 11492
  left_join(Eez_biogeo,
            by = "eezid") %>% 
  left_join(Spp_env_pref,
            by = "taxon_key") %>% 
  left_join(Eez_centroids,
            by = "eezid") %>% 
  mutate(latitude = abs(latitude))

# -------------------------------- #
#### Build models
# -------------------------------- #

# Model 1; all variables
M_all_var <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel + DemersPelag, data = Lm_data)

all_sum <- summary(M_all_var)
all_aic <- AIC(M_all_var)
all_r <-  all_sum$adj.r.squared

# Model 2; non demPel
M2 <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel, data = Lm_data)

M2_sum <- summary(M2)
M2_aic <- AIC(M2)
M2_r <-  M2_sum$adj.r.squared

# Model 3; non biome
M3 <- lm(emerging_yr ~ sst_toe + bot_toe + status + dem_pel + DemersPelag, data = Lm_data)

M3_sum <- summary(M3)
M3_aic <- AIC(M3)
M3_r <-  M3_sum$adj.r.squared

# Model 4; non status
M4 <- lm(emerging_yr ~ sst_toe + bot_toe + biome + dem_pel + DemersPelag, data = Lm_data)

M4_sum <- summary(M4)
M4_aic <- AIC(M4)
M4_r <-  M4_sum$adj.r.squared

# Model 5; non sst
M5 <- lm(emerging_yr ~ status + bot_toe + biome + dem_pel + DemersPelag, data = Lm_data)

M5_sum <- summary(M5)
M5_aic <- AIC(M5)
M5_r <-  M5_sum$adj.r.squared

# Model 6; all + basin
M6 <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel + DemersPelag, data = Lm_data)

M6_sum <- summary(M6)
M6_aic <- AIC(M6)
M6_r <-  M6_sum$adj.r.squared

# Model 7; Categories instead of status
M7 <- lm(emerging_yr ~ sst_toe + bot_toe + category + biome + dem_pel + DemersPelag, data = Lm_data)

M7_sum <- summary(M7)
M7_aic <- AIC(M7)
M7_r <-  M7_sum$adj.r.squared

# Model 8; All variables + ccentroid lat
M8 <- lm(emerging_yr ~ sst_toe + bot_toe + category + biome + DemersPelag + latitude, data = Lm_data)

M8_sum <- summary(M8)
M8_aic <- AIC(M8)
M8_r <-  M8_sum$adj.r.squared

tibble(
  "model" = paste("M",seq(1,8,1),sep=""),
  "AIC" = c(all_aic,M2_aic,M3_aic,M4_aic,M5_aic,M6_aic,M7_aic,M8_aic),
  "rsquared" = c(all_r,M2_r,M3_r,M4_r,M5_r,M6_r,M7_r,M8_r)
)

# UNIDAS 20282659

# The Winner is M8!

stargazer(M8, title = "Results", align=TRUE)

>>>>

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis",
  "cowplot"
)

@@

EEZ_CellID <- my_path("G", extra_path = "Spatial/V_Lam", name="EEZ_CellID.xlsx", read = TRUE) %>%
  clean_names()
colnames(EEZ_CellID) <- c("eezid","index")

# SAU name relatioal table (Fish For Visa)
sau_clean_names <- my_path("G", extra_path = "Spatial/SAU/", name="SAU_matching_names.csv", read = TRUE)

@@

getEnvVar=function(yr,ensemble,variable){

  filepath <- paste("/Volumes/DATA/DATA/Environmental data/GFDL_CMIP5_Large_Ensemble/All var/ens",ensemble,"/",sep="")

    file = paste(variable,"_",yr,".txt",sep="")
    read_me <- paste(filepath,file,sep="")

    data <- bind_cols(lapply(read_me,FUN= data.table::fread, na.strings = "NA",header=F)
      ) %>% 
      mutate(index = seq(1,259200,1))

    colnames(data) <- c(as.character(ensemble),"index")

    data <- data %>% 
      gather("ensemble","variable",1:length(ensemble)) %>%  # fix it has to be untill 10
      mutate(variable = ifelse(variable == -9999.00000,NA,variable)) # Fixing NAs connotation

@@

  getTemp <- data %>% 
    mutate(ensemble = ensemble,
           year = yr)

  return(getTemp)
}

@@

TempEmer <- function(yrs, hist_y = 2005, variable, ensemble){ # The LAST year of Historical data

  # Load environmental data
  sst_data <- bind_rows(
    lapply(
      yrs,
      getEnvVar, 
      ensemble = ensemble, 
      variable = variable
    )
  ) %>% 
    left_join(index_code,
              by = "index") %>%  # join with EEZ indexes
    select(-lat,-lon,-eez_name) %>% 
    filter(!is.na(eezid)) %>% 
    # Get average temperature per eez
    group_by(ensemble,eezid,year) %>%
    summarise_at(vars("variable"),
                 c(hd_eez_mean=mean),
                 na.rm=T
    ) %>% 
    # estimate 10 years running mean
    group_by(ensemble,eezid) %>% 
    mutate(Rmean = rollmean(x = hd_eez_mean, 
                            10, 
                            align = "right", 
                            fill = hd_eez_mean)
    )

  # Average of 10 years mean of ensemble members results
  mean_sd_index <- sst_data %>% 
    group_by(eezid,year) %>% 
    summarise_at(vars("Rmean"),
                 c(trend=mean,
                   ensemble_sd=sd,
                   n_ens = ~n()

@@

  # Historic data
  historical <- sst_data %>%
    filter(year <= hist_y) %>%
    ungroup() %>%
    # get EEZ time average
    group_by(ensemble,eezid) %>%
    summarise_at(vars("Rmean"),
                 c(hd_temp_mean=mean),
                 na.rm= T
    ) %>% 
    # get ensemble member mean and noice
    group_by(eezid) %>% 
    summarise_at(vars("hd_temp_mean"),
                 c(hist_mean=mean,
                   noise = sd),
                 na.rm = T
    )

  # ----------------------- #
  # Plot for data viz
  # ----------------------- #

  # samp <- sample(mean_sd_index$eezid,30,replace = F)

  # mean_sd_index <- mean_sd_index %>% 
    # filter(eezid %in% samp)

    # plot_data <- mean_sd_index %>% 
  # left_join(historical,
  #           by = "eezid")

  # ggplot() +
  #   geom_line(data = plot_data,
  #             aes(
  #               x = year,
  #               y = trend
  #             )
  #   ) +
  #   geom_ribbon(data = plot_data,
  #               aes(x=year,
  #                   ymin=hist_mean-noise,
  #                   ymax=hist_mean+noise
  #                   ),
  #               alpha = 0.5
  #   ) +
  #   geom_line(data = plot_data,
  #             aes(
  #               x = year,
  #               y = hist_mean
  #               ),
  #             linetype = "dashed"
  #   ) +
  #   facet_wrap(~eezid,
  #              scales = "free") +
  #   # Conditional, will only plot circles if the data exists
  #   geom_point(data = subset(plot_data, trend > (hist_mean+noise) | trend < (hist_mean-noise)),
  #              aes(
  #                x = year,
  #                y = trend,
  #                colour = "red",
  #              ),
  #              shape = 1,
  #              size = 3
  #   ) +
  #   geom_vline(xintercept = hist_y,colour="black",alpha = 0.5) +
  #   scale_x_continuous(breaks = seq(1950,2100,5)) +
  #   theme_classic()

  # Future results
  future <- sst_data %>% 
    filter(year > hist_y) %>% 
    # get ensemble member mean and noice
    group_by(eezid,year) %>% 
    summarise_at(vars("Rmean"),
                 c(trend=mean,
                   f_noise = sd)
    ) %>% 
    group_by(eezid)

  Final_Result <- future %>%
    left_join(historical,
              by = "eezid") %>% 
    mutate(
      tresh_one = ifelse(trend > (hist_mean+noise) | trend < (hist_mean-noise),"One",NA),
      tresh_two = ifelse(trend > (hist_mean+(2*noise)) | trend < (hist_mean-(2*noise)),"Two",NA)
    ) %>%
    gather("tresh","YesNo",tresh_one,tresh_two) %>% 
    filter(!is.na(YesNo)) %>% 
    group_by(eezid,tresh) %>% 
    summarise(emerging_yr = min(year))

  return(Final_Result)
}

sst <- TempEmer(
  yrs = seq(1951,2070,1),
  hist_y = 2005,
  variable = "SST",
  ensemble = seq(102,111,1)
)

write_csv(sst,
          "ToE_sst.csv")

botTemp <- TempEmer(
  yrs = seq(1951,2070,1),
  hist_y = 2005,
  variable = "botTemp",
  ensemble = seq(102,111,1)
)

write_csv(botTemp,
          "ToE_bottemp.csv")

test <- sst %>% 
  filter(tresh == "tresh_one")

hist(test$emerging_yr)

test_map <- World_eez_sf %>% 
  left_join(test,
            by = "eezid") %>% 
  ggplot() +
  geom_sf(
    aes(
      fill = emerging_yr
    )
  )+ scale_fill_viridis(
    limits = c(2000,2070),
    breaks = seq(2000,2070,10)#,
    # direction = -1
  ) +
  my_ggtheme_m() +
  ggsave("botTemp_ToE.png",
         width = 12,
         height = 10,
         units = "in"
  )

@@

# Get taxon list
Taxon_List_emer <- list.files(my_path("R",extra_path = "Emergence_2005"))

# clean names for function
Taxon_List_emer <- gsub("_.*","",Taxon_List_emer)

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List_emer,"_emergence.txt",sep="")

# Clean names to match data
Matching_names <- my_path("G","Spatial/SAU", "matching_names.csv", read = T)

# Species depth clasification

Spp_depth <-fread(paste(my_path("D"),"SAU/SppTaxonName.csv", sep ="")) %>% 
  clean_names()

@@

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid_eck,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  # st_sfc(crs = 4326) %>%
  st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  # mutate(geometry = (geometry + c(18000000,9000000)) %% c(360) - c(18000000,9000000)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES"), quiet = TRUE) %>%
  # sf::st_sf(crs = 4326)
  sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    # option="magma",
    # direction = -1
  ) +
  scale_fill_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    alpha = 0.8
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/fig2ax.png",
  width = 12,
  height = 8,
  units = "in"
  )

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid= eez_id ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

ggplot(subset(Eez_d_hist, tresh == "Tresh_one")) +
  geom_density(
    aes(
      x = value,
      fill = tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  )

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id)

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_rev_",tresh_list[i],".png",sep = "")

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = seq(2100,2000,-25),
      direction = -1
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )

@@
